\thetitle

### 2013-04-13 tfpie/tfpie.tex
some more

Context and contraints: HtDP vs. industrial co-op and subsequent Java courses.

Universe and world \cite{dvanhorn:Felleisen2009Functional}.

\cite{dvanhorn:Felleisen2004Structure}

\cite{dvanhorn:Findler2002DrScheme}

\cite{dvanhorn:Felleisen2001How}

>>>>

This combination sets the constraints in which we designed our
approach.  Our students begin the course with a firm grasp of
data-driven program design, as well as experience with the tools used
in the first course:

\begin{itemize}
  \item the student languages introduced in \emph{How to Design
    Programs}~\cite{dvanhorn:Felleisen2004Structure,
    dvanhorn:Felleisen2001How} as well as the idea of ``language levels'';

  \item the DrRacket programming environment~\cite{dvanhorn:Findler2002DrScheme};

  \item the \texttt{check-expect} testing framework~\cite{local:check-expect};

  \item the ``World'' approach to developing interactive animations
    and games using functional
    programming~\cite{dvanhorn:Felleisen2009Functional}.
\end{itemize}

\noindent
We reuses all of these elements in our approach.

After our course, our students should both (a) be prepared for
subsequent courses in the curriculum, which expect familiarity with
Java and standard Java libraries, (b) be prepared for co-ops in which
they will use industrial-strength languages and tools which will
almost certainly be object-oriented.  More significantly, we aim to
teach the key insights behind the object-oriented approach to program
design.
